Exceedance probability comparison for the simplified Naomi model

### 2023-06-19 src/naomi-simple_exceedance/exceedance.Rmd
Should have second 90 as top row rather than high incidence

exceedance_manuscript_plot <- exceedance_manuscript_plot +
  geom_text(
    data = df_metrics %>% mutate(method = fct_relevel(method, "TMB", "PCA-AGHQ")),
    aes(x = -Inf, y = Inf, label = label),
    size = 3, hjust = 0, vjust = 1.5
  )

>>>>

exceedance_manuscript_plot <- exceedance_manuscript_plot +
  geom_text(
    data = df_metrics %>% mutate(
      method = fct_relevel(method, "TMB", "PCA-AGHQ"),
      indicator = fct_relevel(indicator, "Second 90", "High incidence")    
    ),
    aes(x = -Inf, y = Inf, label = label),
    size = 3, hjust = 0, vjust = 1.5
  )
